---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CountEvents

The goal of `CountEvents` is to take a data frame or Tibble, and two variable names as argument.

It performs data validation, filtering out rows with missing values. Then, counts the number of events in the data, grouped by the two specified variables, and returns the result as a data frame

## Installation

You can install the development version of `CountEvents` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/CountEvents")
```

## Example

This is a basic example which shows you how to use `CountEvents`:

```{r example}
library(CountEvents)
library(palmerpenguins)
suppressPackageStartupMessages(library(dplyr))


### *Using the penguins data*

# How many penguins of each species per island in the data??
specie_by_island <- count_events(penguins, species, island)
print(specie_by_island)

```
