---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CountEvents

The goal of Count Events is to count events in a data frame using two variable

This function takes a data frame or Tibble, and two variable names as arguments. It performs data validation, filtering out rows with missing values. counts the number of events in the data, grouped by the two specified variables, and returns the result as a data frame.

## Installation

You can install the development version of CountEvents from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/assignment-b2-jmfvieira11")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
## Some examples of CountEvents application

# Load different libraries to use in the examples
library(CountEvents)
suppressPackageStartupMessages(library(datateachr)) # <- data for example
suppressPackageStartupMessages(library(palmerpenguins))

#### Using the penguins data
# How many penguins of each species per island in the data??

specie_by_island <- count_events(penguins, species, island)
print(specie_by_island)

### Using the vancouver_tree data

# How many trees of each species by the different genus names in the data?
tress_by_species <- count_events(vancouver_trees, genus_name, species_name)
print(tress_by_species)


###Using the parking_meters data

# How many meter head types per localization in the data?
headtype_by_location <- count_events(parking_meters, geo_local_area, meter_head)
print(headtype_by_location)

```


